Leveraging Diversity to Find Bugs\\ in JavaScript Engines

### 2018-08-24 paper/paper.tex

\subsection{Seed JS files\label{sec:seeds}}~
We selected test files from several public projects from GitHub. We
looked for self-contained tests from JS engine projects, initially
using the GitHub REST API~\cite{github-rest-api}. We noticed that some
of the tests we found depend on external libraries, which not all
engines we use support. We decided to discard those. For example, many
tests we found required a Node.js runtime~\cite{node} for
execution. The main source of test cases is the official
Test262~\cite{tc39-github} conformance test suite for the ECMA262
specification~\cite{ecmas262-spec}. This test suite contains 87\% of
all the tests we used. We also considered test suites of three of the
four engines mentioned in Section~\ref{sec:methodology:engines} and
four other engines. Table~\ref{tab:test-suites} shows the breakdown of
tests we considered. Overall, we found a total of \totfiles{} JS
files. Column ``original'' shows the test cases for each
test suite. We did not consider tests from the \chakra{} repository because they depend
on non-portable objects and notice that the number of tests in
\veight\ is low. That happens because many tests in \veight{} are
inherited from Mozilla and \jsc{}; we discarded those to avoid
repetition and to give credit where it is due. Column
``compile-in-all'' shows the number of test cases for which all four
engines we analyzed do not throw compile-time error. We discarded
tests that manifest compile errors as they clearly indicate missing
features; these tests use non-portable names (\eg{}, \jsc{}'s
\CodeIn{drainMicrotasks()} and \smonkey{}'s \CodeIn{Error.lineNumber})
or use functions that, although being part of the spec, not all
engines currently support. Finally, column ``no-fail-in-all'' shows
the tests for which all engines
pass. Section~\ref{sec:transplantation} discusses these failures, some
of which are indicative of bugs. The tests under this column will be
used to create new, potentially fault-revealing, tests. For that, it
is important to assure that all of them pass.

It is also worth mentioning that some engines use a custom shell to
run tests, including a harness with specific assertions.  For these,
we needed to make small changes in the testing infrastructure to be
able to run the tests uniformly across all engines. More precisely, we
needed to mock non-portable harness functions, which are only
available to certain engines.

 %% The table shows the
 %%    number of test cases in each test suite considered: TC-39
 %%    conformance test suite, suites from engines we analyzed, and
 %%    suites from other engines.

\begin{table}[t]
  \centering
  \caption{\label{tab:test-suites}Number of test cases per
    suite. Column ``original'' shows the original size of the test
    suite, column ``compile-in-all'' shows the number of test cases
    for which engines do not throw compile error (\eg{}, undefined
    name), and column ``no-fail-all'' shows the number of test cases
    that pass in all four engines we analyzed.}
  \begin{tabular}{ccrrr}
    \toprule
    \multirow{2}{*}{Name}      &  \multirow{2}{*}{Source} &
    \multicolumn{3}{c}{\# JS files} \\
    \cline{3-5}
                               &         & original & compile-in-all &  no-fail-in-all \\
    \midrule
    TC-39 (Test262) & \cite{ecma262-conformance-suite} & 31,276 &
    29,846 & 17,639 \\
    \midrule
    \jsc{} & \cite{webkit} & 1,031 & 1,021 & 955\\
    \smonkey\ & \cite{mozilla} & 2,634 & 2,116 & 1,686\\
    \veight{} & \cite{v8} & 75 & 57 & 57\\
    \midrule
    Duktape & \cite{duktape} & 1,195 & 921 & 915\\ 
    \jerry{} & \cite{jerryscript} & 1,951 & 1,878 & 1,837\\
    JSI & \cite{jsi} & 99 & 63 & 63\\
    Tiny-js & \cite{tinyjs} & 49 & 37 & 37\\
    % \chakra{} & \cite{chakracore} & 2632 \\
    \midrule
     &  & \totalTestFiles{} & \totalTestFilesCompileInAll{} & \totalTestFilesPassInAll{}\\
   \bottomrule 
  \end{tabular}
\end{table}

@@

Table~\ref{tab:cross-testing} shows the number of failures observed
for each pair of test suite and engine. The first column shows the
test suites and the first row shows the engines that run those
tests. We use a dash (``-'') to indicate that we did not consider the
combinations that associate a test suite with its parent engine;
failures in those cases would either indicate regressions or flaky
tests as opposed to unknown bugs for that engine. We did not run test
cases that fail on its parent engine in any other engines; we wanted
all tests to pass on their parent engine as that would indicate that
the test case is coherent and can be used. In total, 64 test cases
were discarded for that reason--6 from \jsc{} and 57 from
\smonkey. Furthermore, we required that a test does not manifest
compile errors as we want to focus on bugs in code not in tests. For
that reason, we used the tests listed under the column
``compile-in-all'' from Table~\ref{tab:test-suites}, totalling
\totalTestFilesCompileInAll{} cases. \Mar{can you confirm that we used
  ``compile-in-all'' and not ``origina'' as these numbers
  suggest?}\Fix{In total, 7,029 test files (\ie{}, 38369-31276-64)
  were considered in this experiment, which involved 24,922 test runs
  (\ie, (7029*4)-1021-57-2116).}  Of these, 812 failures were
manifested (3.25\% of the runs) across \textbf{543} distinct files
(7.72\% of the files). We observed from
the table that, considering this dataset, the Mozilla \smonkey\ was
the engine that failed the least whereas the Microsoft engine
\chakra\ failed the most. The \smonkey\ test suite also revealed more
failures than any other, as expected, considering that it is the suite
with more tests (see Table~\ref{tab:test-suites}).

>>>>

\subsection{Seed JS files\label{sec:seeds}}~
We selected test files from several public projects from GitHub. We
looked for self-contained tests from JS engine projects, initially
using the GitHub REST API~\cite{github-rest-api}. We noticed that some
of the tests we found depend on external libraries, which not all
engines we use support. We decided to discard those. For example, many
tests we found required a Node.js runtime~\cite{node} for
execution. The main source of test cases is the official
Test262~\cite{tc39-github} conformance test suite for the ECMA262
specification~\cite{ecmas262-spec}.\Comment{ This test suite contains
  87\% of all the tests we used.} We also considered test suites of
three of the four engines mentioned in
Section~\ref{sec:methodology:engines} and four other engines. Overall,
we selected a total of \totfiles{} JS
files. Table~\ref{tab:test-suites} shows the breakdown of tests we
considered. Column ``original'' shows the number of test cases for
each test suite. We did not consider tests from the \chakra{}
repository because they depend on non-portable objects. Notice that
the number of tests in \veight\ is low. That happens because \veight{}
uses many tests from Mozilla and \jsc{}; we discarded those to avoid
repetition and to give credit where it is due. The columns
``compile-in-all'' and ``no-fail-in-all'' correspond to the test files
used, respectively, in the test transplantaion experiment and the
differential testing experiment.

Column ``compile-in-all'' shows the number of test cases whose
execution does not throw errors because of an undefined variable or
property. We capture these cases by looking for the presence of
\CodeIn{ReferenceError} and \CodeIn{TypeError} in the output. A
\CodeIn{ReferenceError} (respectively, \CodeIn{TypeError}) is raised
when test execution attempts to access an undefined variable
(respectively, property of an object). We discarded those tests to
avoid noise in the experiments as they clearly indicate some missing
feature as opposed to bugs. For example, some tests use non-portable
names (\eg{}, \jsc{}'s \CodeIn{drainMicrotasks()} and \smonkey{}'s
\CodeIn{Error.lineNumber}) or use functions that, albeit part of the
spec, not all engines currently support. We used the tests that lie
within the circle that appears in the table in the evaluation of test
transplantion, \ie{} the set ``compile-in-all'' minus set Test262. We
did not consider tests from the conformance suite as they are more
likely to indicate missing features as opposed to bugs. In addition,
engine developers have access to these test and are encouraged to run
them. Column ``no-fail-in-all'' shows the tests for which all engines
pass. This test set is used in the evaluation of differential
testing. Note that it is a proper subset of the ``compile-in-all''
test set. The tests from this group are used as fuzzing seeds. The
guarantee that they pass in all engines assures that, if discrepancies
occur, they are related to the changes in the input as opposed to the
original cause of failure.

It is also worth mentioning that some engines use a custom shell to
run tests, including a harness with specific assertions.  For that, we
needed to make minor changes in the testing infrastructure to be able
to run the tests uniformly across all engines. More precisely, we
needed to mock non-portable harness functions, which are only
available to certain engines.

\newcommand\marktopleft[1]{%
    \tikz[overlay,remember picture] 
        \node (marker-#1-a) at (0,1.5ex) {};%
}
\newcommand\markbottomright[1]{%
    \tikz[overlay,remember picture] 
        \node (marker-#1-b) at (0,0) {};%
    \tikz[overlay,remember picture,thick,dashed,inner sep=3pt]
        \node[draw,rounded rectangle,fit=(marker-#1-a.center) (marker-#1-b.center)] {};%
}

\begin{table}[t]
  \centering
  \caption{\label{tab:test-suites}Number of test cases per
    suite. Column ``original'' shows the original size of the test
    suite, column ``compile-in-all'' shows the number of test cases
    for which engines do not throw compile error (\eg{}, undefined
    name), and column ``no-fail-all'' shows the number of test cases
    that pass in all four engines we analyzed.}
  \begin{tabular}{ccrrr}
    \toprule
    \multirow{2}{*}{Name}      &  \multirow{2}{*}{Source} &
    \multicolumn{3}{c}{\# JS files} \\
    \cline{3-5}
                               &         & original & compile-in-all &  no-fail-in-all \\
    \midrule
    TC-39 (Test262) & \cite{ecma262-conformance-suite} & 31,276 &
    29,846 & 17,639 \\
    \midrule
    \jsc{} & \cite{webkit} & 1,031 &\marktopleft{c1} 1,021 & 955\\
    \smonkey\ & \cite{mozilla} & 2,634 & 2,116 & 1,686\\
    \veight{} & \cite{v8} & 75 & 57 & 57\\
    \midrule
    Duktape & \cite{duktape} & 1,195 & 921 & 915\\ 
    \jerry{} & \cite{jerryscript} & 1,951 & 1,878 & 1,837\\
    JSI & \cite{jsi} & 99 & 63 & 63\\
    Tiny-js & \cite{tinyjs} & 49 & 37\markbottomright{c1} & 37\\
    % \chakra{} & \cite{chakracore} & 2632 \\
    \midrule
     &  & \totalTestFiles{} & \totalTestFilesCompileInAll{} & \totalTestFilesPassInAll{}\\
   \bottomrule 
  \end{tabular}
\end{table}

@@

Table~\ref{tab:cross-testing} shows the number of failures observed
for each pair of test suite and engine. The first column shows the
test suites and the first row shows the engines that run those
tests. We use a dash (``-'') to indicate that we did not consider the
combinations that associate a test suite with its parent engine;
failures in those cases would either indicate regressions or flaky
tests as opposed to unknown bugs for that engine. We did not run test
cases that fail on its parent engine in any other engine as that would indicate that
the test case could be broken. In total, 64 test cases
were discarded for that reason--6 from \jsc{} and 57 from
\smonkey. Furthermore, we required that a test does not manifest
compile errors as we want to focus on bugs in code not in tests. For
that reason, we used the tests listed under the column
``compile-in-all'' from Table~\ref{tab:test-suites}, totalling
\totalTestFilesCompileInAll{} cases. \Mar{can you confirm that we used
  ``compile-in-all'' and not ``origina'' as these numbers
  suggest?}\Fix{In total, 7,029 test files (\ie{}, 38369-31276-64)
  were considered in this experiment, which involved 24,922 test runs
  (\ie, (7029*4)-1021-57-2116).}  Of these, 812 failures were
manifested (3.25\% of the runs) across \textbf{543} distinct files
(7.72\% of the files). We observed from
the table that, considering this dataset, the Mozilla \smonkey\ was
the engine that failed the least whereas the Microsoft engine
\chakra\ failed the most. The \smonkey\ test suite also revealed more
failures than any other, as expected, considering that it is the suite
with more tests (see Table~\ref{tab:test-suites}).
